### 2023-02-17 analysis/paper/paper.qmd
add Zenodo links

All raw data is available on Zenodo (<https://doi.org/10.5281/zenodo.7648757>).
Analysis scripts, and the source code for the manuscript and
supplementary materials are available as a research compendium<!--Zenodo link-->
using the structure recommended by the **rrtools** R package [@Rrrtools].

>>>>

All raw data is available on Zenodo (<https://doi.org/10.5281/zenodo.7648757>).
Analysis scripts, and the source code for the manuscript and
supplementary materials are available as a research compendium
(<https://doi.org/10.5281/zenodo.7649825>)
using the structure recommended by the **rrtools** R package [@Rrrtools].
